---
title: "Fig 4"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---


```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(data.table)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(here)
library(ggstance)
devtools::load_all(here("code","liver.tools"))
```
Read in Noushin's data for TCGA figure

```{r data}
fig.data <- readRDS(here('data', 'TCGA', 'fig2c_p2_data.rds'))
```

## TCGA copy number

TCGA figure panel -- problems, chromosome widths, making the panel match size of one facet in z-score panel

```{r plot, fig.height= 23, fig.width=8,dev=c("png", "pdf")}
setDT(fig.data)
fig.data[,bin:=as.factor(rev(bin))][]
fig.data$disease<-"TCGA Liver Cancers\n(n = 372)"
plot <- fig.data %>%
    mutate(disease="TCGA Liver Cancers\n(n = 372)") %>%
    ggplot(aes(x=value, y=bin, color=change, fill=change)) +
    facet_grid(arm~disease, scales = 'free_y') + ##,
    ##           switch = 'y')+#, space = 'free')+
    ##facet_wrap(~arm, ncol=1, scales="free_y") + ##
    geom_col() +
    scale_x_continuous() +
    scale_fill_brewer(palette = 'Set1')+
    scale_color_brewer(palette = 'Set1')+
    theme_minimal(base_size=24) +
    theme(strip.text.y = element_text(angle = 0,
                                      hjust = 0.5,
                                      vjust = 0.5,
                                      size=20),
          strip.text.x=element_text(size=20),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          panel.grid =  element_blank(),
          legend.title = element_blank(),
          legend.position="bottom") +
    xlab("Proportion of\ncases with CNV") +
    ylab("Chromosome Arm")
```

## Liver study z-scores

The z-score's with our data panel. Problems -- chromosome width.

```{r z_scores}
features <- read_csv(here("data","delfi_features.csv"),
                     show_col_types=FALSE)
meta <- read_csv(here("data", "Clinical_Metadata_spreadsheet_8_11.csv"),
                 show_col_types=FALSE)
meta$grp_id<-sapply(strsplit(meta$id,"P"),"[",1)

d_c<-meta %>% filter(forveryclean==1 & Disease == "Non-cancer")
d_c$cat<-"Danish Cocos"
cirr<-meta %>% filter(forveryclean==1 & Disease == "Cirrhosis")
cirr$cat<-"Cirrhosis"
hbv<-meta %>% filter(forveryclean==1 & Disease == "HBV")
hbv$cat<-"HBV"
hcv<-meta %>% filter(forveryclean==1 & Disease == "HCV")
hcv$cat<-"HCV"
hcc<-meta %>% filter(forveryclean==1 & Disease == "HCC")
hcc$cat<-"HCC"
d1<-rbind(hcc,cirr,hbv,d_c,hcv)
d1<- d1 %>% mutate(cat=if_else(Disease=="HCV"|Disease=="HBV" & Cirrhosisstatus=="no","Viral Hepatitis",cat))
d1<- d1 %>% mutate(cat=if_else(Disease=="HCV" & Cirrhosisstatus=="yes","Cirrhosis",cat))
d1<- d1 %>% mutate(cat=if_else(Disease=="Non-cancer","Non-cancer",cat))
meta<-d1
meta$Disease<-meta$cat
meta<-meta %>% mutate(`HCC Status`=if_else(`HCCStatus`=="Yes","Yes","No"))


cols <- brewer.pal(7,"Set1")
cols[3] <- cols[4]
features2 <- zscore_features(features, meta) %>%
    select(id, hcc_status, Disease, Arm,
           z, root2, root3, y, colors, transp)
###YOU ARE HERE AFTER LUNCH!!!
ns <- features2 %>%
    group_by(hcc_status) %>%
    summarize(n=length(unique(id))) %>%
    mutate(label=paste0(hcc_status, "\n(n = ", n, ")"))
ns <- setNames(ns$label, ns$hcc_status)

zplot_cancer <- features2 %>%
    ggplot(aes(x=y, y=z, color=colors, alpha=transp)) +
    geom_point(size=5) +
    facet_grid(Arm ~ hcc_status, scales = 'free_y',labeller=labeller(hcc_status=ns)) +
    coord_flip() +
    theme_minimal(base_size=24) +
    theme(strip.text.y.left = element_text(angle = 0,
                                           hjust = 0.5,
                                           vjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),

          panel.grid =  element_blank(),
          plot.title = element_blank(),
          legend.title = element_blank(),
          axis.title.y=element_blank(),
          legend.position = "bottom",
          strip.text.y = element_blank()) +
    scale_y_continuous(limits = c(-150,150)) +
    scale_alpha_identity() +
    scale_fill_manual(values = cols) +
    scale_color_manual(values = cols) +
    ylab("Z-Score")
```

Adding together the TCGA and z-score panel -- problems -- chromosome width, size of TCGA panel, not yet stacked with feature importance panel.

```{r cowplot, eval=FALSE}
#pdf("test.pdf")
cowplot::plot_grid(plot,zplot_cancer,nrow=1,align="v",axis="l")
#dev.off() #
```

## Feature importance

Feature importance panel
```{r heatmap}

results<-readRDS(here("output","feature_importance_TF.Rmd",
                     "loadings_TF_screening.rds"))
pd <- results[["pd"]]
sc <- results[["sc"]]
#---------------- now make plots -----------------###
                                        # visualize feature by PC heatmap ##
pc.labels <- c("PC1\n", "PC2\n", "PC3\n") %>%
    setNames(1:3)
heatmap <- pd %>%
    ggplot(aes(x = pc.id, y = bin.id)) +
    facet_grid(arm ~ pc.id, scales = 'free',
               switch = 'y', space = 'free',
               labeller=labeller(pc.id=pc.labels))+
    geom_tile(aes(fill = value)) +
    scale_fill_distiller(palette = 'RdBu') +
    scale_y_continuous(trans = 'reverse') +
    theme_minimal(base_size=24) +
    labs(x = 'Principal components\nof fragmentation profiles', y = '', fill = 'Value') +
    theme(axis.text.x=element_text(color="white"),
          strip.text.y=element_blank(),
          strip.text.x=element_text(size=26),
          axis.text.y = element_text(color="white"),
          axis.title.y=element_text(color="white"),
          axis.ticks = element_blank(),
          panel.grid =  element_blank(),
          legend.position = 'none') +
    ylab("Something")
```

```{r top_annotation}
ta <- top_annotation(sc)

### NEW STUFF
#results2<-readRDS(here("output","feature_importance_TF.Rmd",
                     #"loadings_TF.rds"))
#sc2 <- results2[["sc"]]
#sc2<-sc2 %>% filter(features %in% c("PC 1","PC 2", "PC 3")) 

#ta$model<-"DELFI"
#ta$pc.id<-factor(ta$pc.id,levels=c(2,3,1,2.1,3.1,1.1))
#t<-tibble(pc.id=c(2,3,1),abs.value=sc2$abs.value,sign.value=sc2$sign.value,x=c(1,1,1),model=c("DELFI+TF","DELFI+TF","DELFI+TF"),arm=c(1,1,1))
#ta<-as_tibble(rbind(ta,t))

cols <- c('#0571b0', '#ca0020', '#999999')
names(cols) <- c('-1', '1', NA)
top.annot <- ta %>%
    ggplot(aes(x = pc.id, y = abs.value, colour = sign.value)) +
    facet_grid(arm ~ pc.id, scales = 'free',
                   switch = 'y', space = 'free') +
    geom_point(size = 5) +
    geom_segment(aes(x = pc.id,
                     xend = pc.id,
                     y = abs.value, yend = 0),
                 size=2) +
    theme_minimal(base_size=24) +
    ylab("Log odds ratio") +
    xlab("") +
    theme(axis.text.x=element_text(color="white"),
          strip.text.y=element_blank(),
          axis.line.x=element_line(color="gray"),
          axis.ticks.x=element_line(color="gray"),
          axis.ticks = element_blank(),
          panel.grid =  element_blank(),
          legend.position = 'none') +
##    theme(panel.grid=element_blank(),
##          strip.text.y = element_blank(),

##          strip.text.x = element_blank(),
##          axis.text.x = element_blank(),
##          axis.ticks = element_blank(),
##          panel.border = element_rect(color = "white",
##                                      fill = NA, size = 0.2),
##          legend.position = 'none') +
    scale_color_manual(values = cols, na.value = '#999999')
```

```{r side_annotation}
bins5mb <- read_csv(here("data","long_bins.csv"),
                    show_col_types=FALSE)
sa <- side_annotation(pd, sc, bins5mb)


#sa2 <- results2[["sc"]]
#sa2<-sa2 %>% filter(! features %in% c("PC 1","PC 2", "PC 3","TF_pc_1")) 
#pd2 <- results2[["pd"]]
#sa_temp <- side_annotation(pd2, sc2, bins5mb)$arm.imp
#x <- strsplit(as.character(sa2$features), " " )

#sa2$arm<-sapply( x, "[", 2 )
#sa2<-left_join(sa_temp %>% select(-abs.value),sa2 %>% select(arm,abs.value,scaled_coefs),by="arm")
#sa2 <- sa2 %>% mutate(abs.value=if_else(is.na(abs.value),0,abs.value))
#sa2<-sa2 %>% mutate(sign.value=sign(scaled_coefs))
#sa2 <- sa2 %>% select(-scaled_coefs)

bl <- sa[["bl"]]
arm.imp <- sa[["arm.imp"]]
#arm.imp$model<-"DELFI"
#sa2$model<-"DELFI+TF"
#arm.imp<-rbind(arm.imp,sa2)
right.annot <- bl %>%
    ggplot(aes(x = x, y = bin.id)) +
    geom_point(color = 'white') +
    facet_grid(arm ~ pc.id,
               scales = 'free',
               switch = 'y', space = 'free') +
    theme_minimal(base_size=24) +
    geom_point(data = arm.imp,
               aes(x = abs.value,
                   y = bin.id, color = sign.value),
               size=5) +
    geom_segment(data = arm.imp,
                 aes(x = abs.value, xend = 0,
                     y = bin.id, yend = bin.id,
                     color = sign.value),
                 size=2) +
    scale_color_manual(values = cols, na.value = '#999999') +
    scale_y_continuous(breaks = c(0,2,4,6)) +
    labs(x = 'Log odds\nratio', y = '', color = '') +
    theme(strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          panel.border = element_blank(),
          panel.grid=element_blank(),
          legend.position = 'none')



```

```{r tf_annotation}
sa <- tf_annotation(pd, sc, bins5mb)
sa<-sa[["arm.imp"]]
sa<-sa %>%arrange(abs.value)
sa$arm<-factor(sa$arm,levels=sa$arm)
tf_annotation<-ggplot(sa,aes(x=arm,y=abs.value,color=sign.value))+geom_point(size=5)+geom_segment(data=sa,aes(x=arm,xend=arm,y=abs.value,yend=0,color=sign.value),size=2)+ scale_color_manual(values = cols, na.value = '#999999') +theme_minimal(base_size=24)+ labs(y = 'Log odds\nratio', x = 'TFBS', color = '') +
    theme(strip.text.x = element_blank(),
          strip.text.y = element_blank(),
          axis.text.y = element_text(size=30),
          axis.ticks = element_blank(),
          panel.border = element_blank(),
          panel.grid=element_blank(),
          legend.position = 'none')+coord_flip() 

```




## Fig 4

Assembling the 3 pieces of the feature importance figure into one panel

```{r heights, fig.height=23, fig.width=10, dev=c("png", "pdf")}
hmap <- ggplotGrob(heatmap)
z.coef <- ggplotGrob(right.annot)
pc.coef <- ggplotGrob(top.annot)
h <- hmap$heights
## I think these widths correspond to the panels
ix <- seq(from=8, by=2, length.out=39)
## make logical
is_arm <- seq_along(h) %in% ix
h2 <- h[is_arm]
size <- map_dbl(h2, function(x) unlist(x)[[1]])
## The widths less than 100 might be too small
is2small <- size < 12
h2[is2small] <- unit(12, "null")
h[is_arm] <- h2
z.coef$heights = h
hmap$heights <- h
hmap$widths <- pc.coef$widths
#saveRDS(h, file="../data/arm_heights.rds")
```

```{r eval=FALSE}
##pc.coef$widths = hmap$widths
tf<-ggplotGrob(tf_annotation)
tf$widths<-z.coef$widths
gl <- list(pc.coef,
           hmap,
           z.coef,
           tf)
#gl <- list(pc.coef,
#           hmap,
#           z.coef,
#           nullGrob())

m <- rbind(c(1, 4),
           c(2, 3))
grid.arrange(grobs=gl,
             layout_matrix=m,
             heights=c(1, 7),
             widths=c(4, 1),
             padding=unit(0, "lines"))
```

```{r fig4, fig.height=25, fig.width=28, dev=c("png", "pdf")}
tf<-ggplotGrob(tf_annotation)
#tf$widths<-z.coef$widths
#tf$heights<-z.coef$heights
tcga.legend <- cowplot::get_legend(plot)
p2 <- plot +
    guides(fill="none", color="none") +
    ylab("")
g1 <- ggplotGrob(p2)
g1$heights <- h

zscore.legend <- cowplot::get_legend(zplot_cancer)
p3 <- zplot_cancer +
    guides(color="none", fill="none")
g2 <- ggplotGrob(p3)
g2$heights <- h
gl <- list(g1,
           g2,
           pc.coef,
           hmap,
           z.coef,
           nullGrob(),tf)
m <- rbind(c(6, 6, 3, 6,6),
           c(1, 2, 4, 5,7))
grid.arrange(grobs=gl,
             layout_matrix=m,
             heights=c(1, 7),
             widths=c(2.7, 4, 4, 2.7,2.3),
             padding=unit(0, "lines")) ##
```

